Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-02-27 main.tex
add draft notes for introduction paragraphs
add draft notes for related work

\section{Introduction}

\section{Related work}

>>>>

\section{Introduction}
\draft{
Why is raw waveform modeling interesting?

\wvtwo is very successful and uses neural \fe.

Comparable to other neural feature extraction methods, but not closely studied in the literature.
Maybe some references or name some works which are similar.

Highlight contributions of this paper.
}

\section{Related work}
\draft{
Works on raw waveform acoustic modeling.

Different \wv papers \cite{facebook2019wav2vec, facebook2019vqwav2vec, facebook2020wav2vec2, facebook2020xlsr}.
Describe differences between the approaches.
Besides modifications of the self-supervised training criteria -- moving from the future time step prediction in \cite{facebook2019wav2vec} to masked time step prediction -- and incorporating quantization modules, also the architecture has been revised.
Fully convolutional vs. \transformer.
Differences in \fe.

Think about how to properly reference \cite{vieting2021waveform} without disclosing author information.
}
